Self-sustained carbon monoxide oxidation oscillations on size-selected platinum nanoparticles at atmospheric pressure

### 2012-04-18 paper.tex
Further changes to the article

\begin{scheme}
  \includegraphics[width=12cm]{temperature_dependence.png}
  \caption{After about 10 hours of oscillations at 205$^\circ$C the temperature is first lowered by 5$^\circ$C and soon after increased by 2$^\circ$C. Before the temperature step the oscillation period was approximately 500\,s and after the step the period is approximately 5000\,s.}
  \label{fgr:temperature_dependence}
\end{scheme}

@@

\begin{scheme}
  \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is now supporimposed by small discontinous stpes when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{scheme}

\begin{scheme}
  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue). The temperature is constant $210^\circ$C doing the entire measurement. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{scheme}

>>>>

\begin{scheme}
  \includegraphics[width=12cm]{temperature_dependence.png}
  \caption{Illustration of the strong temperature dependence. After about 10 hours of steady oscillations at 205$^\circ$C the temperature is lowered by 5$^\circ$C immediately decreasing the oscillation frequency. The temperature is hereafter increased by 2$^\circ$C resulting in an increase in oscillation frequency. At 205$^\circ$C the oscillation period was approximately 500\,s while the oscillation period period is approximately 5000\,s. at 203$^\circ$C}
  \label{fgr:temperature_dependence}
\end{scheme}

@@

\begin{figure}
  \includegraphics[width=12cm]{oscillations_gas_dependence_summary_supplemental.png}
  \caption{Summary of the gas-dependence. The overall trend of increasing oscillation period is superimposed with small discontinuous steps when the CO concentration is increased.}
  \label{fgr:gas_dependence_summary}
\end{figure}

\begin{figure}
  \includegraphics[width=14cm]{oscillations_gas_dependence_supplemental.png}
  \caption{Complete series of oscillating sample, showing CO (red) and CO$_2$ (blue). The temperature is constant $210^\circ$C doing the entire measurement. For every frame the CO-concentration is increased.}
  \label{fgr:gas_dependence}
\end{figure}
